\documentclass{article}                                                                                                      
\usepackage{gvv}                                                                                                             
\title{\underline{PRMO-2018}}                                                                                                
\date{}                                                                                                                        
\begin{document}                                                                                                               
\maketitle                                                                                                                     
\begin{enumerate}
\item A book is published in three volumes, the pages being numbered from $1$ onwards. The page numbers are continued from the first volume to the second volume to the third. The number of pages in the second volume is $50$ more than that in the first volume, and the number pages in the third volume is one and a half times that in the second. The sum of the page numbers on the first pages of the three volumes is $1709.$ If n is the last page number, what is the largest prime factor of $n?$ 
\item  In a quadrilateral $ABCD,$ it is given that$ AB = AD = 13,BC = CD = 20,BD = 24.$ If r is the radius of the circle inscribable in the quadrilateral, then what is the integer closest to $r?$
\item  Consider all $6$-digit numbers of the form abccba where b is odd. Determine the number of all such $6$-digit numbers that are divisible by $7.$ 
\item The equation $166 \times 56 = 8590$ is valid in some base $b \geq 10$ (that is, 1, 6, 5, 8, 9, 0 are digits in base b in the above equation). Find the sum of all possible values of $ b \geq 10 $ satisfying the equation. 
\item  Let $ ABCD $ be a trapezium in which $ AB \parallel CD $ and $AD \perp AB.$ Suppose $ABCD$ has an incircle which touches $ AB $at $ Q$ and $ CD $ at $P$. Given that $PC = 36$ and $QB = 49$, find $PQ.$ 
\item Integers $a, b, c$ satisfy $a + b - c =1$ and $a^{2} + b^{2} - c^{2} = -1.$ What is the sum of all possible values of $a^{2} + b^{2} + c^{2}?$
\item  A point P in the interior of a regular hexagon is at distances $8,8,16$ units from three consecutive vertices of the hexagon, respectively. If r is radius of the circumscribed circle of the hexagon, what is the integer closest to $r?$ 
\item  Let $AB$ be a chord of a circle with centre $O.$ Let $C$ be a point on the circle such that $\angle{ABC} = 30^{\circ}$ and $O$ lies inside the triangle $ABC.$ Let $D$ be a point on $AB$ such that $\angle{DCO} = \angle{OCB} = 20^{\circ}$. Find the measure of $\angle{CDO}$ in degrees. 
\item  Suppose $a, b$ are integers and $a+b$ is a root of $x^{2} + ax + b =0. $What is the maximum possible value of $b^{2}?$ 
\item  In a triangle $ABC,$ the median from $B$ to $ CA $ is perpendicular to the median from $C$ to $AB$. If the median from $A$ to $BC$ is $30$, determine ${(BC^{2} +CA^{2} +AB^{2})}/100.$ 
\item There are several tea cups in the kitchen, some with handles and the others without handles. The number of ways of selecting two cups without a handle and three with a handle is exactly $1200.$ What is the maximum possible number of cups in the kitchen$?$
\item Determine the number of $8$-tuples $\brak{\epsilon_1, \epsilon_2, ·· · , \epsilon_8}$ such that $\epsilon_1, \epsilon_2, ·· · \epsilon_8$ $\in \brak{1, -1 }$and $\epsilon_1 +2\epsilon_2 +3\epsilon_3 + ·· · +8 \epsilon_8$
is a multiple of $3.$ 
\item  In a triangle $ABC,$ right-angled at$A$, the altitude through $A$ and the internal bisector of $A$ have lengths $3$ and $ 4$, respectively. Find the length of the median through $A$. 
\item If $ x = \cos 1^\circ \cdot \cos 2^\circ \cdot \cos 3^\circ \cdot \ldots \cdot \cos 89^\circ$ and $y = \cos 2^\circ \cdot \cos 6^\circ \cdot \cos 10^\circ \cdot \ldots \cdot \cos 86^\circ$.We are asked to find the integer nearest to $\frac{2}{7} \log_2 \left( \frac{y}{x} \right)$ $?$
\item  Let $a$ and $b$ be natural numbers such that $2a - b,$ $a - 2b$ and $a + b$ are all distinct squares. What is the smallest possible value of b$?$ 
\item What is the value of $\sum_{1 \leq i < j \leq 10, \, i + j \, \text{ = odd}} (i + j) - \sum_{1 \leq i < j \leq 10, \, i + j \, \text{ = even}} (i + j). ?$
\item Triangles $ABC$ and $DEF$ are such that $\angle{A} = \angle{D,} AB = DE = 17, BC = EF = 10$ and $AC - DF = 12.$ What is $AC +DF?$ 
\item  If $a, b, c \geq 4$ are integers, not all equal, and $ 4abc =(a+3)(b+3)(c+3),$ then what is the value of $ a + b + c?$ 
\item  Let $N = 6 + 66 + 666 +...... + 666 ..... 66,$ where there are hundred $6’$s in the last term in the sum. How many times does the digit $7$ occur in the number $N?$ 
\item  Determine the sum of all possible positive integers $n,$ the product of whose digits equals $n^{2} - 15n - 27.$ 
\item  Let $ABC$ be an acute-angled triangle and let $H$ be its orthocentre. Let $G1, G2 $ and $G3$ be the centroids of the triangles $HBC, HCA $ and $ HAB,$ respectively. If the area of triangle $G_1G_2G_3 $is $7$ units, what is the area of triangle $ABC?$
\item  A positive integer $k$ is said to be good if there exists a partition of \brak{1, 2, 3,. .., 20} in to disjoint proper subsets such that the sum of the numbers in each subset of the partition is $k.$ How many good numbers are there$?$
\item  What is the largest positive integer $n$ such that $ \frac{a^2}{\frac{b}{29} + \frac{c}{31}} + \frac{b^2}{\frac{a}{29} +\frac{c}{31}} + \frac{c^2}{\frac{a}{29} + \frac{b}{31}} \geq$  $ n (a + b + c) $ holds for all positive real numbers $a, b, c.$ 
\item  If $N$ is the number of triangles of different shapes (i.e., not similar) whose angles are all integers (in degrees), what is $\frac{N}{100}?$ 
\item  Let T be the smallest positive integer which, when divided by $11, 13, 15$ leaves remainders in the sets  \cbrak{7, 8, 9},\cbrak {1, 2, 3},\cbrak {4, 5, 6} respectively. What is the sum of the squares of the digits of T$?$ 
\item  What is the number of ways in which one can choose $60$ unit squares from a $11 \times 11 $ chessboard such that no two chosen squares have a side in common$?$
\item What is the number of ways in which one can colour the squares of a $4\times4$ chessboard with colours red and blue such that each row as well as each column has exactly two red squares and two blue squares$?$ 
\item  Let $N$ be the number of ways of distributing $8$ chocolates of different brands among $3$ children such that each child gets at least one chocolate, and no two children get the same number of chocolates. Find the sum of the digits of $N.$
\item  Let $D$ be an interior point of the side $ BC $ of a triangle $ ABC $. Let $ I_1 $ and $ I_2 $ be the incentres of triangles $ ABD $ and $ ACD $ respectively. Let $ AI_1 $ and $ AI_2 $ meet $ BC $ in $ E $ and $ F $ respectively. If $ \angle BI_1E = 60^\circ $, what is the measure of $ \angle CI_2F$ in degrees $?$
\item Let $P(x)= a_0 + a_1x+ a_2x^{2} +........ + ax^{n} $  be a polynomial in which ai is a non-negative integer for each $ i \in \cbrak {0, 1, 2, 3, ·· · ,n}$. If $P(1) = 4$ $P(5) = 136$, what is the value of $P(3)?$
\end{enumerate}
\end{document}
